Sample-efficient Reinforcement Learning \\ with Implicitly Quantized Representations

### 2024-02-01 paper/main.tex
Abstract

\begin{abstract}
  % Deep reinforcement learning (RL) has shown much promise for solving real-world continuous control problems.
  % Whilst deep reinforcement learning (RL) is a competitive approach for solving real-world continuous control problems, it
  % is limited by its sample-efficiency.
  % Recent works have shown that learning representations can improve sample efficiency in RL, whilst also
  % handling complex/high-dimensional observation spaces.
  Learning representations for reinforcement learning (RL) has shown much promise for continuous control.
  Not only can it handle complex observation spaces but it can also improve sample efficiency.
  % Recent works have shown that learning representations can improve sample efficiency in RL.
  A particularly promising approach is to use a self-supervised loss, known as the latent-state consistency loss.
  It requires an encoder which maps observations to latent states and a transition model which predicts
  next latent states.
  It then minimizes the distance between the next state predicted by the transition model and
  the next state predicted by the encoder.
  Typically it is combined with other loss terms such as reward or value prediction.
  This prevents representation collapse at the cost of learning a task-specific representation.
  In this work, we show that a careful consideration of the latent space enables us to {\em (i)} learn
  a task-agnostic representation and {\em (ii)} prevent representation collapse, whilst using only the latent-state
  consistency loss.
  % the leverage the latent-state
  % Typically these approaches have unbounded latent spaces and are combined with auxillary loss terms such as minimizing the
  % error of reward or value predictions in the latent space.
  % of an encoder which maps observations to latent states and a transition model which predicts
  % next latent states given a latent state and an action.
  % However, most of th
  We empirically show that our method prevents representation collapse as it maintains matrix rank.
  Our representation learning approach is {\em (i)} simple, {\em (ii)} can be combined with any model-free RL algorithm
  and, {\em (iii)} obtains state-of-the-art results in continuous control benchmarks from DeepMind Control Suite.
  % Moreover, it kk
% This document provides a basic paper template and submission guidelines.
% Abstracts must be a single paragraph, ideally between 4--6 sentences long.
% Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}

>>>>

\begin{abstract}
  % Arno's proposal
  In reinforcement learning (RL) for continuous control, we propose  an efficient representation learning method using a latent-state consistency loss. This approach employs an encoder and a transition model to map observations to latent states and predict future states, respectively. By minimizing discrepancies between these states, we achieve task-agnostic representations and prevent representation collapse using only the consistency loss. Our method is straightforward, compatible with any model-free RL algorithm, and demonstrates state-of-the-art performance in continuous control benchmarks from DeepMind Control Suite.\looseness-1

  % Deep reinforcement learning (RL) has shown much promise for solving real-world continuous control problems.
  % Whilst deep reinforcement learning (RL) is a competitive approach for solving real-world continuous control problems, it
  % is limited by its sample-efficiency.
  % Recent works have shown that learning representations can improve sample efficiency in RL, whilst also
  % handling complex/high-dimensional observation spaces.
  Learning representations for reinforcement learning (RL) has shown much promise for continuous control.
  Not only can it handle complex observation spaces but it can also improve sample efficiency.
  % Recent works have shown that learning representations can improve sample efficiency in RL.
  A particularly promising approach is to use a self-supervised loss, known as the latent-state consistency loss.
  It requires an encoder which maps observations to latent states and a transition model which predicts
  next latent states.
  It then minimizes the distance between the next state predicted by the transition model and
  the next state predicted by the encoder.
  Typically it is combined with other loss terms such as reward or value prediction.
  This prevents representation collapse at the cost of learning a task-specific representation.
  In this work, we show that a careful consideration of the latent space enables us to {\em (i)} learn
  a task-agnostic representation and {\em (ii)} prevent representation collapse, whilst using only the latent-state
  consistency loss.
  % the leverage the latent-state
  % Typically these approaches have unbounded latent spaces and are combined with auxillary loss terms such as minimizing the
  % error of reward or value predictions in the latent space.
  % of an encoder which maps observations to latent states and a transition model which predicts
  % next latent states given a latent state and an action.
  % However, most of th
  We empirically show that our method prevents representation collapse as it maintains matrix rank.
  Our representation learning approach is {\em (i)} simple, {\em (ii)} can be combined with any model-free RL algorithm
  and, {\em (iii)} obtains state-of-the-art results in continuous control benchmarks from DeepMind Control Suite.
  % Moreover, it kk
% This document provides a basic paper template and submission guidelines.
% Abstracts must be a single paragraph, ideally between 4--6 sentences long.
% Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}
